Cluster Difference Imaging Photometric Survey (CDIPS) II. TOI$\,$837: A Validated Saturn-Sized Planet in IC~2602

### 2020-07-15 paper/authors.tex
update manuscript

% begin (ASTEP team)
\author{L. Abe} % Lyu
\affiliation{Universit\'e C\^{o}te d'Azur, Observatoire de la C\^ote d'Azur, CNRS, Laboratoire Lagrange, Bd de l'Observatoire, CS 34229, 06304 Nice cedex 4, France}

\author{A. Agabi} % Abdelkrim 
\affiliation{Universit\'e C\^{o}te d'Azur, Observatoire de la C\^ote d'Azur, CNRS, Laboratoire Lagrange, Bd de l'Observatoire, CS 34229, 06304 Nice cedex 4, France}

\author[0000-0001-7866-8738]{N. Crouzet} % Nicolas
\affiliation{European Space Agency, European Space Research and Technology Centre (ESA/ESTEC), Keplerlaan 1, 2201 AZ Noordwijk, The Netherlands}

\author[0000-0002-3937-630X]{G. Dransfield} % Georgina
\affiliation{School of Physics \& Astronomy, University of Birmingham, Edgbaston, Birmingham B15 2TT, United Kingdom}

\author[0000-0002-7188-8428]{T. Guillot} % Tristan 
\affiliation{Universit\'e C\^{o}te d'Azur, Observatoire de la C\^ote d'Azur, CNRS, Laboratoire Lagrange, Bd de l'Observatoire, CS 34229, 06304 Nice cedex 4, France}

\author{W. Marie-Sainte} % Wenceslas
\affiliation{Institut Paul \'{E}mile Victor, Concordia Station, Antarctica}

\author{D. M\'ekarnia} % Djamel
\affiliation{Universit\'e C\^{o}te d'Azur, Observatoire de la C\^ote d'Azur, CNRS, Laboratoire Lagrange, Bd de l'Observatoire, CS 34229, 06304 Nice cedex 4, France}

\author[0000-0002-5510-8751]{A. H.M.J. Triaud} % Amaury
\affiliation{School of Physics \& Astronomy, University of Birmingham, Edgbaston, Birmingham B15 2TT, United Kingdom}
% end (ASTEP team)

@@

\author{T. Henning} %Thomas henning@mpia.de FEROS, WINE board
\affiliation{Max-Planck-Institut f\"{u}r Astronomie, K\"onigstuhl 17, Heidelberg 69117, Germany }

\author[0000-0002-9158-7315]{R. Brahm} %rafael.brahm@uai.cl coordination, WINE board
\affiliation{Facultad de Ingenier\'{i}a y Ciencias, Universidad Adolfo Ib\'a\~nez, Av.\ Diagonal las Torres 2640, Pe\~nalol\'en, Santiago, Chile}
\affiliation{Millennium Institute for Astrophysics, Chile}

\author[0000-0001-9513-1449]{N. Espinoza} %N\'estor nespinoza@stsci.edu WINE board
\affiliation{Space Telescope Science Institute, 3700 San Martin Drive, Baltimore, MD 21218, USA}

\author[0000-0002-5389-3944]{A. Jord\'an} %andres.jordan@gmail.com WINE board
\affiliation{Facultad de Ingenier\'{i}a y Ciencias, Universidad Adolfo Ib\'a\~nez, Av.\ Diagonal las Torres 2640, Pe\~nalol\'en, Santiago, Chile}
\affiliation{Millennium Institute for Astrophysics, Chile}

\author{M. Barbieri} %Maruo mauro.barbieri@uda.cl FEROS observations
\affiliation{INCT, Universidad de Atacama, calle Copayapu 485, Copiap\'o, Atacama, Chile}

\author{S. Nandakumar} %sangeetha.nandakumar@postgrados.uda.cl  FEROS observations
\affiliation{INCT, Universidad de Atacama, calle Copayapu 485, Copiap\'o, Atacama, Chile}

\author{T. Trifonov} %Trifon trifonov@mpia.de FEROS observations
\affiliation{Max-Planck-Institut f\"{u}r Astronomie, K\"onigstuhl 17, Heidelberg 69117, Germany }

\author{J. Vines} %Jose jose.vines.l@gmail.com FEROS observations
\affiliation{Departamento de Astronom\'ia, Universidad de Chile, Camino El Observatorio 1515, Las Condes, Santiago, Chile}

\author{M. Vuckovic} %Maja maja.vuckovic@uv.cl FEROS observations
\affiliation{Instituto de F\'isica y Astronom\'ia, Universidad de Vapara\'iso, Casilla 5030, Valpara\'iso, Chile}

%
% SG4 contributors
%
\author[0000-0002-0619-7639]{C.~Ziegler} % carl.ziegler@dunlap.utoronto.ca
\affiliation{Dunlap Institute for Astronomy and Astrophysics,
	University of Toronto, 50 St. George Street, Toronto, Ontario M5S 3H4,
	Canada}

%FIXME ORCIDs
\author{C.~Brice\~{n}o} % cbriceno@ctio.noao.edu
\affiliation{Cerro Tololo Inter-American Observatory, Casilla 603, La
	Serena, Chile}

\author{N.~Law} % nlaw@unc.edu
\affiliation{Department of Physics and Astronomy, The University of
	North Carolina at Chapel Hill, Chapel Hill, NC 27599-3255, USA}

\author{A.~W.~Mann} % awmann@unc.edu
\affiliation{Department of Physics and Astronomy, The University of
	North Carolina at Chapel Hill, Chapel Hill, NC 27599-3255, USA}

% 
%-------------------------------------
% TESS Mission Architects:
% These authors should be listed in this order
% see https://spacebook.mit.edu/pages/viewpage.action?pageId=24543276
%-------------------------------------
%
%PENDING
\author{G. R. Ricker} % grr@space.mit.edu
\affiliation{Department of Physics and Kavli Institute for Astrophysics
and Space Research, Massachusetts Institute of Technology, Cambridge, MA
02139, USA}
%
%PENDING
\author[0000-0001-6763-6562]{R. Vanderspek} % roland@space.mit.edu
\affiliation{Department of Physics and Kavli Institute for Astrophysics
and Space Research, Massachusetts Institute of Technology, Cambridge, MA
02139, USA}
%
%PENDING
\author[0000-0001-9911-7388]{D. W.~Latham} % dlatham@cfa.harvard.edu
\affiliation{Center for Astrophysics \textbar \ Harvard \&
Smithsonian, 60 Garden St, Cambridge, MA 02138, USA}
%
%PENDING
\author{S. Seager} % seager@mit.edu
\affiliation{Department of Earth, Atmospheric, and Planetary Sciences,
Massachusetts Institute of Technology, Cambridge, MA 02139, USA}
%
%PENDING
\author[0000-0002-4715-9460]{J. M.~Jenkins} % jon.jenkins@nasa.gov
\affiliation{NASA Ames Research Center, Moffett Field, CA 94035, USA}
%
%-------------------------------------
% 3 representatives of each of SPOC, POC, TSO, for a total of 9. 
%These 9 authors should be listed in alphabetical order
%-------------------------------------
% 3 TSO COAUTHORS
%     Karen Collins karenacollins@outlook.com
%     Sam Quinn squinn@cfa.harvard.edu
%     Dana Louie danalouie@astro.umd.edu
% 3 SPOC COAUTHORS
%     Mark E. Rose mark.rose@nasa.gov
%     Jeffrey C. Smith  jeffrey.c.smith-1@nasa.gov
%     Bill Wohler  bill.wohler@nasa.gov
% 3 POC COAUTHORS: 
%     John Doty (jpd@noqsi.com)
%     Joel Villaseñor (jsvilla@space.mit.edu)
%     Tom Barclay (barclay.astro@gmail.com)

\author{TSO/SPOC/POC representatives}

>>>>

% begin (ASTEP team)
%PENDING
\author{L. Abe} % Lyu
\affiliation{Universit\'e C\^{o}te d'Azur, Observatoire de la C\^ote d'Azur, CNRS, Laboratoire Lagrange, Bd de l'Observatoire, CS 34229, 06304 Nice cedex 4, France}

%PENDING
\author{A. Agabi} % Abdelkrim 
\affiliation{Universit\'e C\^{o}te d'Azur, Observatoire de la C\^ote d'Azur, CNRS, Laboratoire Lagrange, Bd de l'Observatoire, CS 34229, 06304 Nice cedex 4, France}

%PENDING
\author[0000-0001-7866-8738]{N. Crouzet} % Nicolas
\affiliation{European Space Agency, European Space Research and Technology Centre (ESA/ESTEC), Keplerlaan 1, 2201 AZ Noordwijk, The Netherlands}

%PENDING
\author[0000-0002-3937-630X]{G. Dransfield} % Georgina
\affiliation{School of Physics \& Astronomy, University of Birmingham, Edgbaston, Birmingham B15 2TT, United Kingdom}

%PENDING
\author[0000-0002-7188-8428]{T. Guillot} % Tristan 
\affiliation{Universit\'e C\^{o}te d'Azur, Observatoire de la C\^ote d'Azur, CNRS, Laboratoire Lagrange, Bd de l'Observatoire, CS 34229, 06304 Nice cedex 4, France}

%PENDING
\author{W. Marie-Sainte} % Wenceslas
\affiliation{Institut Paul \'{E}mile Victor, Concordia Station, Antarctica}

%PENDING
\author{D. M\'ekarnia} % Djamel
\affiliation{Universit\'e C\^{o}te d'Azur, Observatoire de la C\^ote d'Azur, CNRS, Laboratoire Lagrange, Bd de l'Observatoire, CS 34229, 06304 Nice cedex 4, France}

%PENDING
\author[0000-0002-5510-8751]{A. H.M.J. Triaud} % Amaury
\affiliation{School of Physics \& Astronomy, University of Birmingham, Edgbaston, Birmingham B15 2TT, United Kingdom}
% end (ASTEP team)

@@

%PENDING
\author{T. Henning} %Thomas henning@mpia.de FEROS, WINE board
\affiliation{Max-Planck-Institut f\"{u}r Astronomie, K\"onigstuhl 17, Heidelberg 69117, Germany }

%PENDING
\author[0000-0002-9158-7315]{R. Brahm} %rafael.brahm@uai.cl coordination, WINE board
\affiliation{Facultad de Ingenier\'{i}a y Ciencias, Universidad Adolfo Ib\'a\~nez, Av.\ Diagonal las Torres 2640, Pe\~nalol\'en, Santiago, Chile}
\affiliation{Millennium Institute for Astrophysics, Chile}

%PENDING
\author[0000-0001-9513-1449]{N. Espinoza} %N\'estor nespinoza@stsci.edu WINE board
\affiliation{Space Telescope Science Institute, 3700 San Martin Drive, Baltimore, MD 21218, USA}

%PENDING
\author[0000-0002-5389-3944]{A. Jord\'an} %andres.jordan@gmail.com WINE board
\affiliation{Facultad de Ingenier\'{i}a y Ciencias, Universidad Adolfo Ib\'a\~nez, Av.\ Diagonal las Torres 2640, Pe\~nalol\'en, Santiago, Chile}
\affiliation{Millennium Institute for Astrophysics, Chile}

%PENDING
\author{M. Barbieri} %Maruo mauro.barbieri@uda.cl FEROS observations
\affiliation{INCT, Universidad de Atacama, calle Copayapu 485, Copiap\'o, Atacama, Chile}

%PENDING
\author{S. Nandakumar} %sangeetha.nandakumar@postgrados.uda.cl  FEROS observations
\affiliation{INCT, Universidad de Atacama, calle Copayapu 485, Copiap\'o, Atacama, Chile}

%PENDING
\author{T. Trifonov} %Trifon trifonov@mpia.de FEROS observations
\affiliation{Max-Planck-Institut f\"{u}r Astronomie, K\"onigstuhl 17, Heidelberg 69117, Germany }

%PENDING
\author{J. Vines} %Jose jose.vines.l@gmail.com FEROS observations
\affiliation{Departamento de Astronom\'ia, Universidad de Chile, Camino El Observatorio 1515, Las Condes, Santiago, Chile}

%PENDING
\author{M. Vuckovic} %Maja maja.vuckovic@uv.cl FEROS observations
\affiliation{Instituto de F\'isica y Astronom\'ia, Universidad de Vapara\'iso, Casilla 5030, Valpara\'iso, Chile}

%
% SG4 contributors
%
%PENDING
\author[0000-0002-0619-7639]{C.~Ziegler} % carl.ziegler@dunlap.utoronto.ca
\affiliation{Dunlap Institute for Astronomy and Astrophysics, University of Toronto, 50 St. George Street, Toronto, Ontario M5S 3H4, Canada}

%PENDING
\author{C.~Brice\~{n}o} % cbriceno@ctio.noao.edu
\affiliation{Cerro Tololo Inter-American Observatory, Casilla 603, La Serena, Chile}

%PENDING
\author{N.~Law} % nlaw@unc.edu
\affiliation{Department of Physics and Astronomy, The University of North Carolina at Chapel Hill, Chapel Hill, NC 27599-3255, USA}

%PENDING
\author{A.~W.~Mann} % awmann@unc.edu
\affiliation{Department of Physics and Astronomy, The University of North Carolina at Chapel Hill, Chapel Hill, NC 27599-3255, USA}

% 
%-------------------------------------
% TESS Mission Architects:
% These authors should be listed in this order
% see https://spacebook.mit.edu/pages/viewpage.action?pageId=24543276
%-------------------------------------
%
%PENDING
\author{G. R. Ricker} % grr@space.mit.edu
\affiliation{Department of Physics and Kavli Institute for Astrophysics and Space Research, Massachusetts Institute of Technology, Cambridge, MA 02139, USA}
%
%PENDING
\author[0000-0001-6763-6562]{R. Vanderspek} % roland@space.mit.edu
\affiliation{Department of Physics and Kavli Institute for Astrophysics and Space Research, Massachusetts Institute of Technology, Cambridge, MA 02139, USA}
%
%PENDING
\author[0000-0001-9911-7388]{D. W.~Latham} % dlatham@cfa.harvard.edu
\affiliation{Center for Astrophysics \textbar \ Harvard \& Smithsonian, 60 Garden St, Cambridge, MA 02138, USA}
%
%PENDING
\author{S. Seager} % seager@mit.edu
\affiliation{Department of Earth, Atmospheric, and Planetary Sciences, Massachusetts Institute of Technology, Cambridge, MA 02139, USA}
%
%PENDING
\author[0000-0002-4715-9460]{J. M.~Jenkins} % jon.jenkins@nasa.gov
\affiliation{NASA Ames Research Center, Moffett Field, CA 94035, USA}

%
%-------------------------------------
% 3 representatives of each of SPOC, POC, TSO, for a total of 9. 
%These 9 authors should be listed in alphabetical order
%-------------------------------------

%PENDING
\author[0000-0002-7754-9486]{C~J.~Burke} % cjburke@mit.edu
\affiliation{Department of Physics and Kavli Institute for Astrophysics and Space Research, Massachusetts Institute of Technology, Cambridge, MA 02139, USA}

%PENDING
\author[0000-0003-2313-467X]{D.~Dragomir}
\affiliation{Department of Physics and Astronomy, University of New Mexico, Albuquerque, NM, USA}

%PENDING
\author[0000-0003-0918-7484]{C.~X.~Huang}
\affiliation{Department of Physics and Kavli Institute for Astrophysics and Space Research, Massachusetts Institute of Technology, Cambridge, MA 02139, USA}

%PENDING
\author{R.~C.~Kidwell, Jr.} % rkidwell@stsci.edu
\affiliation{Space Telescope Science Institute, 3700 San Martin Drive, Baltimore MD 21218 }

%PENDING
\author{A.~M.~Levine} % aml@space.mit.edu
\affiliation{Department of Physics and Kavli Institute for Astrophysics and Space Research, Massachusetts Institute of Technology, Cambridge, MA 02139, USA}

%PENDING
\author{E. Quintana} % elisa.quintana@nasa.gov
\affiliation{NASA Goddard Space Flight Center, 8800 Greenbelt Road, Greenbelt, MD 20771, USA}

%PENDING
\author[0000-0001-8812-0565]{J.~E.~Rodriguez}
\affiliation{Center for Astrophysics \textbar \ Harvard \& Smithsonian, 60 Garden St, Cambridge, MA 02138, USA}

%PENDING
\author[0000-0002-6148-7903]{J. C. Smith} % jeffrey.c.smith-1@nasa.gov
\affiliation{NASA Ames Research Center, Moffett Field, CA 94035, USA}
\affiliation{SETI Institute, Mountain View, CA 94043, USA}

%PENDING
\author[0000-0002-5402-9613]{B. Wohler} % bill.wohler@nasa.gov
\affiliation{NASA Ames Research Center, Moffett Field, CA 94035, USA}
\affiliation{SETI Institute, Mountain View, CA 94043, USA}

### 2020-07-15 paper/ms.tex
update manuscript

%
% TODO:
% * remove all bf todo's
%

@@

To derive the stellar parameters, we matched the set of CHIRON spectra
against a library of observed spectra, previously
obtained using the Tillinghast Reflect Echelle Spectrograph
\citep[TRES,][]{furesz_tres_2008} on the 1.5\,m reflector at the Fred
Lawrence Whipple Observatory (FLWO), Arizona, US, and classified using
the Stellar Parameter Classification pipeline
\citep{buchhave_hatp16b_class_2010}.  We found the best matching
stellar parameters to be $T_\mathrm{eff} = 5899 \pm 55$K, $\log g =
4.496 \pm 0.011$ dex, and $\mathrm{[Fe/H]} -0.069 \pm 0.042$ dex.
% TODO note to Zhou: inflated Fe/H uncertainty by factor of 2.

@@

\subsubsection{Not SB2}
We determined our detection limits to blended spectroscopic companions
using the CHIRON spectra (see Section~\ref{subsec:chiron}).  For a
slowly rotating stellar companion well-separated in velocity, this
would have revealed companions with flux fractions $F_2/F_1 \gtrsim
3\%$.  For a companion with rotational broadening of $15\,{\rm
km\,s}^{-1}$, roughly equivalent to that of \tn, we were able to
exclude companions with flux fractions exceeding $\approx$8\%.  For
plotting purposes, in Figure~\ref{fig:fpscenario} we have assumed the
latter flux-fraction limit of 8\% ($\Delta {\rm mag} \approx 2.7$).
For bound companions this is justified through reasoning that coeval
binary companions to \tn\ would have both longer rotation periods and
smaller stellar radii, and therefore smaller equatorial velocities.

@@

The above exercise ruled out the possibility that the observed
eclipses are caused by a stellar-mass object orbiting \tn.  The lack
of a linear trend in the radial velocities, particularly in the FEROS
data, further constrains the presence of a hierarchical binary system.
To derive limits for this second possibility, we placed a wide
log-uniform prior on the semi-amplitude and period ($\log K\ [{\rm
m\,s^{-1}}] \sim \mathcal{U}(1,10^5)$, $\log P\ [{\rm days}] \sim
\mathcal{U}(0.1, 10^{15})$).  We then fitted for the semi-amplitude,
period, time of conjunction, instrument offsets, and jitter
parameters.  We converted the resulting posterior in period and
semi-amplitude to minimum mass and semi-major axis assuming Kepler's
third law.  The resulting $3\sigma$ limits are shown in
Figure~\ref{fig:fpscenario}.
{\it LGB TODO: the procedure in the preceding paragraph might be modified to
	instead convert the FEROS limit $|\dot{\gamma}| < 0.82\,{\rm m\,s}^{-1}\,{\rm
		day}^{-1}$ directly into a semi-amplitude limit.}

>>>>

%
% TODO:
% * gammadot second method check
%

@@

To derive the stellar parameters, we matched the set of CHIRON spectra
against a library of observed spectra, previously
obtained using the Tillinghast Reflect Echelle Spectrograph
\citep[TRES,][]{furesz_tres_2008} on the 1.5\,m reflector at the Fred
Lawrence Whipple Observatory (FLWO), Arizona, US, and classified using
the Stellar Parameter Classification pipeline
\citep{buchhave_hatp16b_class_2010}.  We found the best matching
stellar parameters to be $T_\mathrm{eff} = 5899 \pm 55$K, $\log g =
4.496 \pm 0.011$ dex, and $\mathrm{[Fe/H]} -0.069 \pm 0.042$ dex.

@@

\subsubsection{Not SB2}
We determined our detection limits to blended spectroscopic companions
using the CHIRON spectra (see Section~\ref{subsec:chiron}).  For a
slowly rotating stellar companion well-separated in velocity, this
would have revealed companions with flux fractions $F_2/F_1 \gtrsim
3\%$.  For a companion with rotational broadening of $15\,{\rm
km\,s}^{-1}$, roughly equivalent to that of \tn, we were able to
exclude companions with flux fractions exceeding $\approx$8\%.  For
plotting purposes, in Figure~\ref{fig:fpscenario} we have assumed the
latter flux-fraction limit of 8\% ($\Delta {\rm mag} \approx 2.7$).
For bound companions this is justified through reasoning that coeval
binary companions to \tn\ would have both longer rotation periods and
smaller stellar radii. The equatorial velocities of such companions
would therefore be expected to be smaller than that of \tn.

@@

The above exercise ruled out the possibility that the observed
eclipses are caused by a stellar-mass object orbiting \tn.  The lack
of a linear trend in the radial velocities, particularly in the FEROS
data, further constrains the presence of a hierarchical binary system.
To derive limits for this second possibility, we placed a wide
log-uniform prior on the semi-amplitude and period ($\log K\ [{\rm
m\,s^{-1}}] \sim \mathcal{U}(1,10^5)$, $\log P\ [{\rm days}] \sim
\mathcal{U}(0.1, 10^{15})$).  We then fitted for the semi-amplitude,
period, time of conjunction, instrument offsets, and jitter
parameters.  We converted the resulting posterior in period and
semi-amplitude to minimum mass and semi-major axis assuming Kepler's
third law.  The resulting $3\sigma$ limits are shown in
Figure~\ref{fig:fpscenario}.
{\it LGB NOTE: the procedure in the preceding paragraph might be modified to
	instead convert the FEROS limit $|\dot{\gamma}| < 0.82\,{\rm m\,s}^{-1}\,{\rm
		day}^{-1}$ directly into a semi-amplitude limit.}
